disaggregation: An \proglang{R} package for Bayesian spatial disaggregation modelling

### 2019-12-02 article.Rnw
Minor edits to likelihood text

%
\begin{itemize}
\item {\textbf{Gaussian} ($\sigma_i$ is the dispersion of the polygon data)
\begin{equation} \label{eq:gaussian}
y_i \sim \textrm{Normal}(\textrm{cases}_i, \sigma_i)
\end{equation}
Here $\sigma_i = \sigma \sqrt{\sum_j a_{ij}^2}$, where  $\sigma$ is the pixel-level dispersion (a parameter learnt by the model) }

\item \textbf{Binomial} (For a survey in polygon $i$, $y_i$ is the number positive cases and $M_i$ is the number tested),
\begin{equation} \label{eq:binomial}
y_i \sim \textrm{Binomial}(M_i, \textrm{rate}_i)
\end{equation}

\item \textbf{Poisson} (predicts incidence count),
\begin{equation} \label{eq:poisson}
y_i \sim \textrm{Pois}(\textrm{cases}_i)
\end{equation}

>>>>

%
\begin{itemize}
\item {\textbf{Gaussian}
\begin{equation} \label{eq:gaussian}
y_i \sim \textrm{Normal}(\textrm{cases}_i, \sigma_i)
\end{equation}
Here $\sigma_i = \sigma \sqrt{\sum_j a_{ij}^2}$, where  $\sigma$ is the pixel-level dispersion (a parameter learnt by the model) }

\item \textbf{Binomial}
\begin{equation} \label{eq:binomial}
y_i \sim \textrm{Binomial}(M_i, \textrm{rate}_i)
\end{equation}
For a survey in polygon $i$, $y_i$ is the number positive cases and $M_i$ is the number tested.

\item \textbf{Poisson}
\begin{equation} \label{eq:poisson}
y_i \sim \textrm{Pois}(\textrm{cases}_i)
\end{equation}
